Simulation Study: Informative Covariate (cosine)

### 2018-07-23 datasets/simulations/simulations-informative-cosine.Rmd
Add cosine informative covariate sim

---
title: "Simulation Study: Informative Covariate (step)"
author: "Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
   html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

In this set of simulations, we consider settings with both null and non-null
tests with an informative covariate. The covariate is sampled uniformly from
the interval [0, 1], and the conditional probability of a test being non-null
is a non-smooth (monotone) step function of the covariate. We include simulation results
again with Gaussian, t-distributed, and Chi-Squared distributed noise.

@@

## intermediary files we create below
gauss_file <- file.path(resdir, "informative-step-benchmark-gaussian.rds")
tdist_file <- file.path(resdir, "informative-step-benchmark-t5.rds")
tdist11_file <- file.path(resdir, "informative-step-benchmark-t11.rds")
chisq_file <- file.path(resdir, "informative-step-benchmark-chisq4.rds")

@@

```{r parameters-shared}
m <- 20000                        # integer: number of hypothesis tests
pi0 <- pi0_step(0.90)             # numeric: proportion of null hypotheses
icovariate <- runif               # functional: independent covariate
```

>>>>

---
title: "Simulation Study: Informative Covariate (cosine)"
author: "Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
   html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

In this set of simulations, we consider settings with both null and non-null
tests with an informative covariate. The covariate is sampled uniformly from
the interval [0, 1], and the conditional probability of a test being non-null
is a smooth (cosine) function of the covariate. We include simulation results
again with Gaussian, t-distributed, and Chi-Squared distributed noise.

@@

## intermediary files we create below
gauss_file <- file.path(resdir, "informative-cosine-benchmark-gaussian.rds")
tdist_file <- file.path(resdir, "informative-cosine-benchmark-t5.rds")
tdist11_file <- file.path(resdir, "informative-cosine-benchmark-t11.rds")
chisq_file <- file.path(resdir, "informative-cosine-benchmark-chisq4.rds")

@@

```{r parameters-shared}
m <- 20000                        # integer: number of hypothesis tests
pi0 <- pi0_cosine(0.90)           # numeric: proportion of null hypotheses
icovariate <- runif               # functional: independent covariate
```
